---
title: "Data X - ARIMA"
author: "Sabrina Le"
date: "4/25/2019"
output: github_document
---
```{r}
library(dplyr)
library(astsa)
library(TSA)
library(forecast)
library(ggplot2)
crypto <- read.csv("/Users/sabrinaa_le/Downloads/baseline_def_kaggle.csv")
```


```{r}
btc <- crypto %>%
  select(close, X)
btc$X <- btc$X+1
ggplot(data = btc, aes(x = X, y = close)) + geom_line() + ggtitle("Bitcoin Closing Price Over Time") + xlab("Time Index") + ylab("BTC Closing Price")
```


```{r}
#ARIMA model
auto.arima(log(btc$close), trace = TRUE)
```
```{r, fig.show="hide", results="hide"}
#evaluate ARIMA forecast values
vec <- 0
se <- 0
for (i in 150:1798) {
  mod_df <- btc[1:i, ]
  modpred <- sarima.for(log(mod_df$close), 1, 0, 1, 0, 0, 0, 0, 0)
  vec[(i - 149)] <- modpred$pred
  se[(i - 149)] <- modpred$se
}

lower <- vec - 2*se
upper <- vec + 2*se
modmod <- btc$close[151:1799]
actual <- log(modmod)
sum(actual < lower) + sum(actual > upper)
a <- which(actual < lower)
b <- which(actual > upper)
btc_mod <- c(a, b)
index <- 1:length(vec)
df <- data.frame(index, actual, vec, "act" = exp(actual), "vecexp" = exp(vec))
```

##Plot of Significant Events & Residuals

In the graph below, every red dot symbolizes an anomaly. In this ARIMA case, an anomaly is an event in which the log of predicted BTC closing price is more than 2 SDs away from the log of the actual BTC closing price. After fitting an ARIMA model on the data, we discovered that 100 events were detected, which is 5.55% of the data, validating our 5% target in our naive approaches.

We also graphed the residuals and plotted them against time. After taking the top 2.5% of the biggest residuals and flagging those as anomalies, we found out that most significant events happened during the Bitcoin bubble. 
```{r}
ggplot(df, aes(x=index , y=act)) + 
  #geom_line(aes(x = index, y = act), colour="red") +
  geom_line(aes(x = index, y = vecexp)) +
  geom_point(data=df[btc_mod,], aes(x=index, y=vecexp), colour="red", size=0.6) + 
  ggtitle("Significant Events using ARIMA") +
  xlab("Time Index") +
  ylab("BTC Closing Price")

#residuals
resid <- exp(actual) - exp(vec)
df$resid <- resid
crypto_mod <- crypto[151:1799,]
df$sd <- crypto_mod$X7.Day.SD
anomaly <- which(abs(resid) >= 2*df$sd)
ggplot(df, aes(index, abs(resid))) + 
  geom_point(size = 0.6) + 
  #geom_point(data = df[anomaly,], aes(x = index, y=abs(resid)), colour = "red") + 
  ggtitle("Residuals vs. Time") + 
  xlab("Time Index") + 
  ylab("Residuals") #+ geom_line(aes(index, 2*sd), col = "blue")                    

nrow(df) * 0.05
sort_resid <- order(abs(df$resid), decreasing = TRUE)
sort_resid <- sort_resid[1:82]

ggplot(df, aes(index, abs(resid))) + 
  geom_point(size = 0.6) + 
  geom_point(data = df[sort_resid,], aes(x = index, y=abs(resid)), colour = "red", size = 0.75) + 
  ggtitle("Residuals vs. Time") + 
  xlab("Time Index") + 
  ylab("Absolute Value of Residuals") #+ geom_line(aes(index, 2*sd), col = "blue")

ggplot(df, aes(x=index , y=act)) +
  geom_line(aes(x = index, y = vecexp)) +
  geom_point(data=df[sort_resid,], aes(x=index, y=vecexp), colour="red", size=1) + 
  ggtitle("Significant Events by Residual Ranking") +
  xlab("Time Index") +
  ylab("BTC Closing Price")
```






